A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-03-05 analysis/paper/paper_latex.Rmd
remove comments from end

This report was generated on `r Sys.time()` using `r devtools:::platform_info()$version` and the following packages:
```{r colophon, cache = FALSE}
devtools::session_info()$packages %>% knitr::kable()
```
Maybe add a figure here showing the real outputs of some methods(which are very method specific and not so easy to compare), and how they can nicely be compared when using your common visualisation tool?
We will do that in V2 for sure! Thanks!
And maybe maybe if someone finds the time this evening :)
In the next version of the paper, an overview of all the errors produced by a method and an overview of all of the timings should be provided.
For the next version of the paper, explain the different metrics (and the common trajectory format) with one supplementary figure, like figure evaluation_overview/metric_geodesic.tmp.pdf

>>>>

This report was generated on `r Sys.time()` using `r devtools:::platform_info()$version` and the following packages:
```{r colophon, cache = FALSE}
devtools::session_info()$packages %>% knitr::kable()
```
